---
title: Fam file release check
author: Christian Coffman
date: today
format:
  html:
    code-fold: true
    embed-resources: true
---

Author: Christian Coffman
Date Created: 25-10-09
Last Updated: 25-10-17
[Further information](https://docs.google.com/document/d/1dYBvSBbSGM_-6453IT4EZkIUkvk6vaVQcLL-FPADz5Y/edit?tab=t.0)


```{bash}
dataDir=/projects/standard/basu_hbcd/shared/HST_HBCD_Transfer_July2025/HBCD/
release=2025october
releaseDir=/projects/standard/basu_hbcd/shared/HBCD_genomics_release_${release}/data/
```


```{r loadData}
#| include: false

library(tidyverse)
library(testthat)
library(kableExtra)

release <- "2025october"
releaseDir <- paste0("/projects/standard/basu_hbcd/shared/HBCD_genomics_release_", release, "/data/")
```


```{r}
#| include: false
library(tidyverse)
library(testthat)
library(kableExtra)
```
- The missing values are from the individual who wasn't deidentified
  - additionally, this individual has an IID starting with "QI" (note that everyone else has IID starting with "CH")


# Comparisons 
```{r}
# Same 
print("Proportion same Sex")
mean(convTable$SEX.original == convTable$SEX.release, na.rm = T) 
print("Proportion same relation")
mean(convTable$relation.original == convTable$relation.release, na.rm = T)
print("Proportion same sex/relation")
mean(interaction(convTable$relation.original, convTable$SEX.original) == interaction(convTable$relation.release, convTable$SEX.release), na.rm = T)


print("Proportion same ID")
mean(convTable$pscid.original == convTable$pscid.release, na.rm = T)
# convTable %>%
#   count(pscid.original, pscid.release) %>%
#   group_by(pscid.original, pscid.release) %>%
#   filter(n() > 1)
# empty table shows that FID is unique mapping between two data tables
```
  - [x] Counts
    - [x] Sex
    - [x] Mother/Child
    - [x] Mother/Child * Sex
    - [x] FID
    - All these counts will contain missingness counts if there are any


  - [x] Order
```{r}
print("Proportion same comparing new vs old order")
mean(convTable$pscid.release == original$pscid)

#temp <- convTable[which(convTable$pscid.release != original$pscid), ]

```

- Everything looks good once we solve the issues associated with the not-yet-deidentified individual

