---
title: "CNV QC Report"
format:
  html:
    embed-resources: true
    code-fold: true
---

```{r}
#| label: setup
#| message: false
library(tidyverse)
library(gridExtra)

CNV_FILE <- "/projects/standard/basu_hbcd/shared/data_handoff/CNV_slim.txt"
DEMO_FILE <- "/projects/regulated/cdni-nih-bdc/shared/data/HBCD/HBCD_prerelease_tabulated_data/phenotype/sed_basic_demographics.tsv"

race_names <- c("0" = "WHT", "1" = "BLK", "2" = "AIAN",
                "3" = "ASN", "4" = "HPI", "5" = "2PLUS",
                "6" = "OTH", "7" = "UNK")

df <- read_tsv(CNV_FILE, show_col_types = FALSE, n_max=1500000) %>%
  mutate(
    type = str_extract(sample_id, "[CM]$"),
    pscid = str_split_i(sample_id, "_", 3)
  )

dm <- read_tsv(DEMO_FILE, show_col_types = FALSE)

# Crosswalk: prerelease pscid → release_candid
IDENTIFIERS_FILE <- "/projects/standard/basu_hbcd/shared/data/release_identifiers_20260526.csv"
ids <- read_csv(IDENTIFIERS_FILE, show_col_types = FALSE) %>%
  filter(release_candid != "release_candid") %>%
  mutate(
    pscid = tolower(as.character(pscid)),
    release_candid = as.character(as.integer(release_candid))
  ) %>%
  distinct(pscid, release_candid)

child_lookup <- dm %>%
  filter(session_id == "ses-V02") %>%
  mutate(participant_id = str_remove(tolower(participant_id), "^sub-")) %>%
  group_by(participant_id) %>%
  summarise(
    race = {
      r <- na.omit(sed_basic_demographics_child_race)
      if (length(r) == 0) "UNK" else race_names[as.character(names(sort(table(r), decreasing = TRUE))[1])]
    },
    .groups = "drop"
  ) %>%
  transmute(
    release_candid = participant_id,
    race = replace_na(race, "UNK")
  )

mother_lookup <- dm %>%
  filter(session_id == "ses-V01") %>%
  mutate(participant_id = str_remove(tolower(participant_id), "^sub-")) %>%
  group_by(participant_id) %>%
  summarise(
    race = {
      r <- na.omit(sed_basic_demographics_screen_mother_race)
      if (length(r) == 0) "UNK" else race_names[as.character(names(sort(table(r), decreasing = TRUE))[1])]
    },
    .groups = "drop"
  ) %>%
  transmute(
    release_candid = participant_id,
    race = replace_na(race, "UNK")
  )

df <- df %>%
  mutate(pscid = tolower(pscid)) %>%
  left_join(ids, by = "pscid") %>%
  left_join(
    bind_rows(
      child_lookup %>% mutate(type = "C"),
      mother_lookup %>% mutate(type = "M")
    ),
    by = c("release_candid", "type")
  ) %>%
  mutate(
    race = replace_na(race, "UNK"),
    b_allele_freq = as.numeric(b_allele_freq)
  )

# GRCh38 chromosome lengths for cumulative genomic position
chrlens <- c(248956422, 242193529, 198295559, 190214555, 181538259,
             170805979, 159345973, 145138636, 138394717, 133797422,
             135086622, 133275309, 114364328, 107043718, 101991189,
             90338345, 83257441, 80373285, 58617616, 64444167,
             46709983, 50818468, 156040895, 57227415)
names(chrlens) <- as.character(c(1:22, "X", "Y"))
chr_offset <- setNames(c(0, cumsum(head(chrlens, -1))), names(chrlens))
chr_boundaries <- cumsum(chrlens)

df <- df %>%
  mutate(
    chr_num = case_when(
      chromosome == "X" ~ 23L,
      chromosome == "Y" ~ 24L,
      TRUE ~ as.integer(chromosome)
    ),
    pos_cum = position + chr_offset[as.character(chr_num)],
  )
```

## Overview

```{r}
#| label: overview
cat("Rows:", scales::comma(nrow(df)), "\n")
cat("Samples:", scales::comma(n_distinct(df$sample_id)), "\n")
cat("Chromosomes:", n_distinct(df$chromosome), "\n")
cat("SNPs:", scales::comma(n_distinct(df$snp_name)), "\n\n")
cat("Missing LRR:       ", scales::comma(sum(is.na(df$log_r_ratio))), "\n")
cat("Missing BAF:       ", scales::comma(sum(is.na(df$b_allele_freq))), "\n")
cat("Missing CNV value: ", scales::comma(sum(is.na(df$cnv_value))), "\n")
cat("Missing confidence:", scales::comma(sum(is.na(df$cnv_confidence))), "\n")
```

## Column Summary

A statistical summary of all numeric columns.

```{r}
#| label: column-summary
df %>%
  select(log_r_ratio, b_allele_freq, cnv_value, cnv_confidence) %>%
  pivot_longer(everything(), names_to = "metric", values_to = "value") %>%
  group_by(metric) %>%
  summarise(
    n       = scales::comma(n()),
    missing = scales::comma(sum(is.na(value))),
    mean    = mean(value, na.rm = TRUE) |> round(4),
    sd      = sd(value, na.rm = TRUE) |> round(4),
    q01     = quantile(value, 0.01, na.rm = TRUE) |> round(4),
    q25     = quantile(value, 0.25, na.rm = TRUE) |> round(4),
    median  = median(value, na.rm = TRUE) |> round(4),
    q75     = quantile(value, 0.75, na.rm = TRUE) |> round(4),
    q99     = quantile(value, 0.99, na.rm = TRUE) |> round(4),
    .groups = "drop"
  ) %>%
  knitr::kable()
```

## Distributions

### Log R Ratio

```{r}
#| label: dist-lrr
#| fig-width: 10
#| fig-height: 4
p1 <- df %>%
  ggplot(aes(log_r_ratio)) +
  geom_histogram(bins = 80, fill = "#1f78b4", alpha = 0.7, colour = "white", linewidth = 0.2) +
  labs(x = "Log R Ratio", y = "Count", title = "LRR distribution") +
  theme_minimal()

p2 <- df %>%
  ggplot(aes(log_r_ratio)) +
  geom_histogram(bins = 80, fill = "#1f78b4", alpha = 0.7, colour = "white", linewidth = 0.2) +
  xlim(-1, 1) +
  labs(x = "Log R Ratio (zoomed)", y = "Count", title = "LRR distribution (-1, 1)") +
  theme_minimal()

grid.arrange(p1, p2, ncol = 2)
```

### B Allele Frequency

```{r}
#| label: dist-baf
#| fig-width: 12
#| fig-height: 4
p1 <- df %>%
  ggplot(aes(b_allele_freq)) +
  geom_histogram(bins = 60, fill = "#33a02c", alpha = 0.7, colour = "white", linewidth = 0.2) +
  labs(x = "BAF", y = "Count", title = "BAF (0, 1)") +
  theme_minimal()

p2 <- df %>%
  ggplot(aes(b_allele_freq)) +
  geom_histogram(bins = 60, fill = "#33a02c", alpha = 0.7, colour = "white", linewidth = 0.2) +
  xlim(0, 0.1) +
  labs(x = "BAF", y = "Count", title = "BAF (0, 0.1)") +
  theme_minimal()

p3 <- df %>%
  ggplot(aes(b_allele_freq)) +
  geom_histogram(bins = 60, fill = "#33a02c", alpha = 0.7, colour = "white", linewidth = 0.2) +
  xlim(0.9, 1) +
  labs(x = "BAF", y = "Count", title = "BAF (0.9, 1)") +
  theme_minimal()

grid.arrange(p1, p2, p3, ncol = 3)
```

### CNV Value and Confidence

```{r}
#| label: dist-cnv
#| fig-width: 10
#| fig-height: 4
p1 <- df %>%
  ggplot(aes(cnv_value)) +
  geom_histogram(bins = 50, fill = "#ff7f00", alpha = 0.7, colour = "white", linewidth = 0.2) +
  labs(x = "CNV value", y = "Count", title = "CNV value") +
  theme_minimal()

p2 <- df %>%
  ggplot(aes(cnv_confidence)) +
  geom_histogram(bins = 50, fill = "#a6cee3", alpha = 0.7, colour = "white", linewidth = 0.2) +
  labs(x = "CNV confidence", y = "Count", title = "CNV confidence") +
  theme_minimal()

grid.arrange(p1, p2, ncol = 2)
```

## Per-Sample Summary

Aggregating SNPs to the sample level to examine variation in coverage and signal quality.

```{r}
#| label: per-sample-stats
per_sample <- df %>%
  group_by(sample_id) %>%
  summarise(
    n_snps    = n(),
    mean_lrr  = mean(log_r_ratio, na.rm = TRUE),
    mean_baf  = mean(b_allele_freq, na.rm = TRUE),
    mean_cnv  = mean(cnv_value, na.rm = TRUE),
    mean_conf = mean(cnv_confidence, na.rm = TRUE),
    .groups   = "drop"
  )

cat("Samples:", scales::comma(nrow(per_sample)), "\n")
cat("SNPs per sample — min:", scales::comma(min(per_sample$n_snps)),
    ", median:", scales::comma(median(per_sample$n_snps)),
    ", max:", scales::comma(max(per_sample$n_snps)), "\n")
```

```{r}
#| label: plot-per-sample
#| fig-width: 10
#| fig-height: 8
p1 <- per_sample %>%
  ggplot(aes(n_snps)) +
  geom_histogram(bins = 40, fill = "#1f78b4", alpha = 0.7, colour = "white", linewidth = 0.2) +
  scale_x_log10(labels = scales::comma) +
  labs(x = "SNPs per sample", y = "Samples") +
  theme_minimal()

p2 <- per_sample %>%
  ggplot(aes(mean_lrr)) +
  geom_histogram(bins = 40, fill = "#33a02c", alpha = 0.7, colour = "white", linewidth = 0.2) +
  labs(x = "Mean LRR per sample", y = "Samples") +
  theme_minimal()

p3 <- per_sample %>%
  ggplot(aes(mean_baf)) +
  geom_histogram(bins = 40, fill = "#ff7f00", alpha = 0.7, colour = "white", linewidth = 0.2) +
  labs(x = "Mean BAF per sample", y = "Samples") +
  theme_minimal()

p4 <- per_sample %>%
  ggplot(aes(mean_cnv)) +
  geom_histogram(bins = 40, fill = "#a6cee3", alpha = 0.7, colour = "white", linewidth = 0.2) +
  labs(x = "Mean CNV value per sample", y = "Samples") +
  theme_minimal()

grid.arrange(p1, p2, p3, p4, ncol = 2)
```

## Per-Chromosome Summary

SNP density and signal quality across chromosomes.

```{r}
#| label: per-chrom
per_chr <- df %>%
  group_by(chromosome) %>%
  summarise(
    n_snps    = n(),
    n_samples = n_distinct(sample_id),
    mean_lrr  = mean(log_r_ratio, na.rm = TRUE),
    mean_baf  = mean(b_allele_freq, na.rm = TRUE),
    mean_cnv  = mean(cnv_value, na.rm = TRUE),
    .groups   = "drop"
  ) %>%
  mutate(chr_num = case_when(
    chromosome == "X" ~ 23L, chromosome == "Y" ~ 24L,
    TRUE ~ as.integer(chromosome)
  )) %>%
  arrange(chr_num)

per_chr %>%
  select(chromosome, n_snps, n_samples, mean_lrr, mean_baf, mean_cnv) %>%
  mutate(across(where(is.numeric), ~ round(.x, 2))) %>%
  knitr::kable()
```

```{r}
#| label: plot-per-chrom
#| fig-width: 10
#| fig-height: 4
per_chr %>%
  mutate(chr = fct_inorder(as.character(chromosome))) %>%
  ggplot(aes(chr, n_snps)) +
  geom_col(fill = "#1f78b4", alpha = 0.8, colour = "white", linewidth = 0.3) +
  geom_text(aes(label = scales::comma(n_snps)), vjust = -0.3, size = 2.8) +
  labs(x = "Chromosome", y = "SNPs") +
  theme_minimal()
```

## Flagged Observations

Potential data-quality issues worth investigation.

```{r}
#| label: flagged
flags <- list()
n_total <- nrow(df)

extreme_lrr <- df |> filter(abs(log_r_ratio) > 2)
if (nrow(extreme_lrr) > 0)
  flags <- c(flags, paste0("|LRR| > 2: ", scales::comma(nrow(extreme_lrr)), " rows (", scales::percent(nrow(extreme_lrr) / n_total, 0.01), ")"))

extreme_baf <- df |> filter(b_allele_freq < 0 | b_allele_freq > 1)
if (nrow(extreme_baf) > 0)
  flags <- c(flags, paste0("BAF outside [0,1]: ", scales::comma(nrow(extreme_baf)), " rows"))

no_conf <- df |> filter(is.na(cnv_confidence))
if (nrow(no_conf) > 0)
  flags <- c(flags, paste0("Missing confidence: ", scales::comma(nrow(no_conf)), " rows (", scales::percent(nrow(no_conf) / n_total, 0.01), ")"))

low_conf <- df |> filter(!is.na(cnv_confidence), cnv_confidence < 0.5)
if (nrow(low_conf) > 0)
  flags <- c(flags, paste0("Confidence < 0.5: ", scales::comma(nrow(low_conf)), " rows (", scales::percent(nrow(low_conf) / n_total, 0.01), ")"))

if (length(flags) > 0) {
  cat("**Potential issues:**\n\n")
  for (f in flags) cat(f, "\n")
} else {
  cat("No significant issues flagged.")
}
```

## C vs M Analysis

Comparing child (C) and mother (M) samples to check for systematic differences.

```{r}
#| label: cm-breakdown
n_c <- sum(df$type == "C", na.rm = TRUE)
n_m <- sum(df$type == "M", na.rm = TRUE)
n_both <- df %>%
  group_by(pscid) %>%
  filter(n_distinct(type) == 2) %>%
  pull(pscid) %>% n_distinct()

cat("C-type rows:", scales::comma(n_c), "\n")
cat("M-type rows:", scales::comma(n_m), "\n")
cat("Unique C samples:", scales::comma(n_distinct(filter(df, type == "C")$sample_id)), "\n")
cat("Unique M samples:", scales::comma(n_distinct(filter(df, type == "M")$sample_id)), "\n")
cat("Participants with both C and M:", scales::comma(n_both), "\n")
```

### LRR by Type

Overlaid density curves to detect systematic LRR shifts between child and mother samples.

```{r}
#| label: cm-lrr
#| fig-width: 10
#| fig-height: 4
p1 <- df %>%
  filter(!is.na(type)) %>%
  ggplot(aes(log_r_ratio, fill = type)) +
  geom_density(alpha = 0.4, colour = NA) +
  scale_fill_manual(values = c("C" = "#1f78b4", "M" = "#e31a1c"), labels = c("C (child)", "M (mother)")) +
  labs(x = "Log R Ratio", y = "Density", fill = NULL, title = "LRR by type (full)") +
  theme_minimal()

p2 <- df %>%
  filter(!is.na(type)) %>%
  ggplot(aes(log_r_ratio, fill = type)) +
  geom_density(alpha = 0.4, colour = NA) +
  xlim(-1, 1) +
  scale_fill_manual(values = c("C" = "#1f78b4", "M" = "#e31a1c")) +
  labs(x = "Log R Ratio", y = "Density", fill = NULL, title = "LRR by type (-1, 1)") +
  theme_minimal()

grid.arrange(p1, p2, ncol = 2)
```

### BAF by Type

```{r}
#| label: cm-baf
#| fig-width: 12
#| fig-height: 4
p1 <- df %>%
  filter(!is.na(type)) %>%
  ggplot(aes(b_allele_freq, fill = type)) +
  geom_density(alpha = 0.4, colour = NA) +
  scale_fill_manual(values = c("C" = "#1f78b4", "M" = "#e31a1c")) +
  labs(x = "BAF", y = "Density", fill = NULL, title = "BAF (0, 1)") +
  theme_minimal()

p2 <- df %>%
  filter(!is.na(type)) %>%
  ggplot(aes(b_allele_freq, fill = type)) +
  geom_density(alpha = 0.4, colour = NA) +
  xlim(0, 0.1) +
  scale_fill_manual(values = c("C" = "#1f78b4", "M" = "#e31a1c")) +
  labs(x = "BAF", y = "Density", fill = NULL, title = "BAF (0, 0.1)") +
  theme_minimal()

p3 <- df %>%
  filter(!is.na(type)) %>%
  ggplot(aes(b_allele_freq, fill = type)) +
  geom_density(alpha = 0.4, colour = NA) +
  xlim(0.9, 1) +
  scale_fill_manual(values = c("C" = "#1f78b4", "M" = "#e31a1c")) +
  labs(x = "BAF", y = "Density", fill = NULL, title = "BAF (0.9, 1)") +
  theme_minimal()

grid.arrange(p1, p2, p3, ncol = 3)
```

### CNV Value and Confidence by Type

```{r}
#| label: cm-box
#| fig-width: 10
#| fig-height: 4
p_cnv <- df %>%
  filter(!is.na(type)) %>%
  ggplot(aes(type, cnv_value, fill = type)) +
  geom_boxplot(alpha = 0.5, outlier.size = 0.3, outlier.alpha = 0.1) +
  scale_fill_manual(values = c("C" = "#1f78b4", "M" = "#e31a1c")) +
  labs(x = NULL, y = "CNV value", fill = NULL) +
  theme_minimal()

p_conf <- df %>%
  filter(!is.na(type)) %>%
  ggplot(aes(type, cnv_confidence, fill = type)) +
  geom_boxplot(alpha = 0.5, outlier.size = 0.3, outlier.alpha = 0.1) +
  scale_fill_manual(values = c("C" = "#1f78b4", "M" = "#e31a1c")) +
  labs(x = NULL, y = "Confidence", fill = NULL) +
  theme_minimal()

grid.arrange(p_cnv, p_conf, ncol = 2)
```

### Paired C-M LRR Correlation

For participants with both a child and mother sample, comparing their mean LRR to identify discordant pairs.

```{r}
#| label: cm-paired
#| fig-width: 8
#| fig-height: 7

paired <- df %>%
  filter(!is.na(type)) %>%
  group_by(pscid, type) %>%
  summarise(mean_lrr = mean(log_r_ratio, na.rm = TRUE), .groups = "drop") %>%
  pivot_wider(id_cols = pscid, names_from = type, values_from = mean_lrr) %>%
  drop_na(C, M)

if (nrow(paired) > 0) {
  r <- cor(paired$C, paired$M, use = "complete.obs")
  lims <- range(c(paired$C, paired$M))

  p <- paired %>%
    mutate(flagged = abs(C - M) > 0.5) %>%
    ggplot(aes(C, M)) +
    geom_abline(slope = 1, intercept = 0, linetype = "dashed", alpha = 0.4) +
    geom_point(aes(colour = flagged), alpha = 0.6, size = 1.5) +
    geom_smooth(method = "lm", se = FALSE, colour = "grey40", linewidth = 0.5) +
    scale_colour_manual(values = c("FALSE" = "#1f78b4", "TRUE" = "#e31a1c")) +
    coord_fixed(xlim = lims, ylim = lims) +
    labs(x = "Mean LRR (C / child)", y = "Mean LRR (M / mother)",
         colour = "|C-M| > 0.5", title = paste0("Paired C vs M LRR (r = ", round(r, 3), ")")) +
    theme_minimal()

  print(p)

  n_flagged <- sum(abs(paired$C - paired$M) > 0.5)
  cat("Paired participants:", scales::comma(nrow(paired)), "\n")
  cat("Pearson r:", round(r, 3), "\n")
  cat("|C - M| LRR > 0.5:", scales::comma(n_flagged), "participants\n")
  if (n_flagged > 0) {
    cat("\n**Flagged participants:**\n\n")
    paired %>%
      filter(abs(C - M) > 0.5) %>%
      mutate(diff = round(abs(C - M), 4)) %>%
      arrange(desc(diff)) %>%
      select(pscid, C, M, diff) %>%
      knitr::kable()
  }
} else {
  cat("*No paired C-M participants found*")
}
```

## Stratified by Race

Race distribution and CNV metrics stratified by reported race, split by child (C) and mother (M) type.

```{r}
#| label: race-breakdown
race_colors <- c("WHT" = "#1f78b4", "BLK" = "#e31a1c", "AIAN" = "#33a02c",
                 "ASN" = "#ff7f00", "HPI" = "#6a3d9a", "2PLUS" = "#b15928",
                 "OTH" = "#cab2d6", "UNK" = "#999999")

df %>%
  filter(!is.na(type)) %>%
  count(race, type) %>%
  pivot_wider(id_cols = race, names_from = type, values_from = n, values_fill = 0) %>%
  arrange(race) %>%
  knitr::kable()
```

### LRR by Race and Type

```{r}
#| label: race-lrr
#| fig-width: 12
#| fig-height: 5
df %>%
  filter(!is.na(type), !is.na(log_r_ratio)) %>%
  ggplot(aes(race, log_r_ratio, fill = type)) +
  geom_boxplot(alpha = 0.5, outlier.size = 0.3, outlier.alpha = 0.1) +
  scale_fill_manual(values = c("C" = "#1f78b4", "M" = "#e31a1c"), labels = c("C (child)", "M (mother)")) +
  labs(x = "Reported race", y = "Log R Ratio", fill = NULL) +
  theme_minimal()
```

### BAF by Race and Type

```{r}
#| label: race-baf
#| fig-width: 12
#| fig-height: 5
df %>%
  filter(!is.na(type), !is.na(b_allele_freq)) %>%
  ggplot(aes(race, b_allele_freq, fill = type)) +
  geom_boxplot(alpha = 0.5, outlier.size = 0.3, outlier.alpha = 0.1) +
  scale_fill_manual(values = c("C" = "#1f78b4", "M" = "#e31a1c"), labels = c("C (child)", "M (mother)")) +
  labs(x = "Reported race", y = "B Allele Frequency", fill = NULL) +
  theme_minimal()
```

### CNV Value and Confidence by Race

```{r}
#| label: race-cnv
#| fig-width: 12
#| fig-height: 5
p1 <- df %>%
  filter(!is.na(type), !is.na(cnv_value)) %>%
  ggplot(aes(race, cnv_value, fill = type)) +
  geom_boxplot(alpha = 0.5, outlier.size = 0.3, outlier.alpha = 0.1) +
  scale_fill_manual(values = c("C" = "#1f78b4", "M" = "#e31a1c"), labels = c("C (child)", "M (mother)")) +
  labs(x = "Reported race", y = "CNV value", fill = NULL) +
  theme_minimal()

p2 <- df %>%
  filter(!is.na(type), !is.na(cnv_confidence)) %>%
  ggplot(aes(race, cnv_confidence, fill = type)) +
  geom_boxplot(alpha = 0.5, outlier.size = 0.3, outlier.alpha = 0.1) +
  scale_fill_manual(values = c("C" = "#1f78b4", "M" = "#e31a1c"), labels = c("C (child)", "M (mother)")) +
  labs(x = "Reported race", y = "Confidence", fill = NULL) +
  theme_minimal()

grid.arrange(p1, p2, ncol = 2)
```

## Genomic Profile

Smoothed trend of each CNV metric across the genome, styled like a Manhattan plot with alternating chromosome bands. Colored by reported race, faceted by age bin and sample type (C/M).

```{r}
#| label: gp-chr-bands
#| fig-width: 14
#| fig-height: 10

chr_bands <- data.frame(
  start = chr_offset,
  end = chr_offset + chrlens,
  fill = ifelse(seq_along(chrlens) %% 2 == 0, "even", "odd"),
  row.names = names(chrlens)
)

chr_labels <- data.frame(
  chr = names(chrlens),
  pos = (chr_offset + chrlens / 2) / 1e6
)

make_genome_plot <- function(data, y_var, y_label) {
  ggplot(data, aes(pos_cum / 1e6, {{ y_var }}, color = race, linetype  = type)) +
    geom_smooth(method = "gam", se = FALSE, linewidth = 0.5, na.rm = TRUE) +
    facet_wrap(~chr_num, scales = "free_x") +
    scale_color_manual(values = race_colors) +
    theme_minimal() +
    theme(
      axis.text.x = element_blank(),
      panel.grid.minor = element_blank(),
      panel.spacing = unit(0.6, "lines"),
      strip.text = element_text(size = 8)
    )
}

p_lrr <- df %>%
  filter(!is.na(type), !is.na(log_r_ratio)) %>%
  make_genome_plot(log_r_ratio, "Log R Ratio")
print(p_lrr)
```

### B Allele Frequency

```{r}
#| label: gp-baf
#| fig-width: 14
#| fig-height: 10
p_baf <- df %>%
  filter(!is.na(type), !is.na(b_allele_freq)) %>%
  make_genome_plot(b_allele_freq, "B Allele Frequency")
print(p_baf)
```

### CNV Value

```{r}
#| label: gp-cnv
#| fig-width: 14
#| fig-height: 10
p_cnv_gp <- df %>%
  filter(!is.na(type), !is.na(cnv_value)) %>%
  make_genome_plot(cnv_value, "CNV Value")
print(p_cnv_gp)
```
