---
title: Fam file release check
author: Christian Coffman
date: today
format:
  html:
    code-fold: true
    embed-resources: true
---

# Load/Process

Goal:
Check if deidentified file contains the same information as the source data.

- [x] Load data
  - July transfer - "ground truth"
  - release - deidentified
  - Identifiers

- original - Original data
- release - data to be released
- identifiers - mappings between original and release
- Didn't include code loading chunk for privacy
  - NOTE: loaded slightly altered files "*_ccEdit*" to deidentify a subject
- [x] Create FID column in original (i.e.e remove M and C)
```{r}
#| include: false
library(tidyverse)
library(testthat)
library(kableExtra)

original <- read_table("/projects/standard/basu_hbcd/shared/HST_HBCD_Transfer_July2025/HBCD/HBCD.fam", col_names= c("FID", "IID", "PAT", "MAT", "SEX", "PHENO")) %>%
  filter(!grepl("_Control_", FID)) %>%
  filter(!grepl("^NTC", FID)) %>%
  mutate(
    FID = str_sub(FID, 1, -2),
    pscid = str_split_i(FID, "_", 3),
    pscidR = paste0(pscid, str_sub(IID, -1, -1))
  )

release <- read_table("/projects/standard/basu_hbcd/shared/HBCD_genomics_release_br_20p0/concat/genetics/genotype_microarray/smokescreen/BR20.0/HBCD_BR20.0.fam", col_names=c("FID", "IID", "PAT", "MAT", "SEX", "PHENO")) %>%
  filter(!grepl("_Control_", FID)) %>%
  filter(!grepl("^NTC", FID))  %>%
  mutate(FID = as.numeric(FID))

identifiers <- read_csv("/projects/standard/basu_hbcd/shared/HBCD_genomics_release_br_20p0/concat/genetics/genotype_microarray/smokescreen/release_identifiers_20251006_ccEdit.csv")
```

- [x] use idenfiers as map: release -> July transfer
  - Make sure order is preserved
  - there are 28 rows corresponding to Positive controls "Positive_control_*" and something else "NTC_*" so I filtered those out for quality checks
  - WARNING: Appears that there is a subject that hasn't been deidentified in the release file!!
    - Removing for now to finish off rest of checks

```{r}
convTable <- release %>%
  left_join(identifiers, by = c("FID" = "release_candid")) %>%
  mutate(
    pscidR = paste0(pscid, str_sub(IID, -1, -1)),
  ) %>%
  full_join(original, by = "pscidR", suffix= c(".release", ".original")) %>%
  mutate(
    relation.release = str_sub(IID.release, -1, -1),
    relation.original = str_sub(IID.original, -1, -1)
  )


# make sure everyone is deidentified
# temp <- release %>%
#   filter(!grepl("_Control_", FID)) %>%
#   filter(!grepl("^NTC", FID)) %>%
#   mutate(
#     fidLength = nchar(FID),
#     iidLength = nchar(IID),
#   ) %>%
#   arrange(desc(fidLength)) %>%
#   head(1)

colSums(is.na(convTable)) %>%
  kable(caption = "Missingness count after joining all of the data sources.")
```
- The missing values are from the individual who wasn't deidentified
  - additionally, this individual has an IID starting with "QI" (note that everyone else has IID starting with "CH")


# Comparisons 
```{r}
# Same 
print("Proportion same Sex")
mean(convTable$SEX.original == convTable$SEX.release, na.rm = T) 
print("Proportion same relation")
mean(convTable$relation.original == convTable$relation.release, na.rm = T)
print("Proportion same sex/relation")
mean(interaction(convTable$relation.original, convTable$SEX.original) == interaction(convTable$relation.release, convTable$SEX.release), na.rm = T)


print("Proportion same ID")
mean(convTable$pscid.original == convTable$pscid.release, na.rm = T)
# convTable %>%
#   count(pscid.original, pscid.release) %>%
#   group_by(pscid.original, pscid.release) %>%
#   filter(n() > 1)
# empty table shows that FID is unique mapping between two data tables
```
  - [x] Counts
    - [x] Sex
    - [x] Mother/Child
    - [x] Mother/Child * Sex
    - [x] FID
    - All these counts will contain missingness counts if there are any


  - [x] Order
```{r}
print("Proportion same comparing new vs old order")
mean(convTable$pscid.release == original$pscid)

#temp <- convTable[which(convTable$pscid.release != original$pscid), ]

```

- Everything looks good once we solve the issues associated with the not-yet-deidentified individual

